### 2018-01-31 includes/introduction.tex
Fixing contributions and footnotes.

\begin{enumerate}
\item \textbf{The \fuzzer{} tool}:
    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can transform and
    randomly generate extremal \smtfull{} string and regular expression
    (regex) problems~\footnote{We assume basic
    familiarity with string solvers and their input
    language.}. Extremal or scaling inputs (e.g., long string
    constants, deep concatenations) are particularly useful in
    identifying asymptotic behaviors in solvers. We briefly document \fuzzer{}'s
    components and modular architecture. We provide example use cases to
    demonstrate its utility as an exploratory tool for validating
    solvers.

>>>>

\begin{enumerate}
\item \textbf{The \fuzzer{} tool}:
    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
    transform and randomly generate \smtfull{} string and regular
    expression (regex) problems.\footnote{We assume basic
    familiarity with string solvers and their input
    language.} Scaling inputs (e.g., long string
    constants, deep concatenations) are particularly useful in
    identifying asymptotic behaviors in solvers, and \fuzzer{}.
    We briefly document \fuzzer{}'s
    components and modular architecture. We provide example use cases to
    demonstrate its utility as an exploratory tool for validating
    solvers.

### 2018-01-31 includes/problems.tex
Centering and putting tables at the top.
Fixing contributions and footnotes.

We generated several suites
of string and regex problems using \fuzzer{}\footnote{The link to the
repository will be added after double-blind review.}.
Table~\ref{tbl:generated} describes the suite
\texttt{generated} by \generator{}.
\begin{table}[H]
    \centering
    \caption{\generator{}-generated problem sets.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}             & \textbf{Problems have ...} \\ \hline
        \textit{Concats}          & A single, deep tree of concats. \\ \hline
        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
    \end{tabular}
\end{table}

@@

The \texttt{transformed}
suite contains benchmarks derived from existing seed problems by
iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows
the overview. Every problem in the suite is named according to its
seed and the transformations it undertook. For example, input
\texttt{seed-fuzz-graft.smt2} was transformed by applying
\texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
\begin{table}[H]
    \centering
    \caption{Transformed problem sets generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}   & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
        \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
        \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
    \end{tabular}
\end{table}

>>>>

We generated several suites
of string and regex problems using \fuzzer{}.\footnote{The link to the
repository will be added after double-blind review.}
Table~\ref{tbl:generated} describes the suite
\texttt{generated} by \generator{}.
\begin{table}[t]
    \centering
    \caption{\generator{}-generated problem sets.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}             & \textbf{Problems have ...} \\ \hline
        \textit{Concats}          & A single, deep tree of concats. \\ \hline
        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
    \end{tabular}
\end{table}

@@

The \texttt{transformed}
suite contains benchmarks derived from existing seed problems by
iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows
the overview. Every problem in the suite is named according to its
seed and the transformations it undertook. For example, input
\texttt{seed-fuzz-graft.smt2} was transformed by applying
\texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
\begin{table}[t]
    \centering
    \caption{Transformed problem sets generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}   & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
        \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
        \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
    \end{tabular}
\end{table}
